 %& -job-name=jaimetrovoada_resume

\documentclass[a4paper, 20pt]{article}

\title{Resume}
\author{Jaime Trovoada Dias Lourenco}
\date{July 2022}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{CJKutf8}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\familydefault}{\sfdefault}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom{}
\raggedright{}
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}
\begin{CJK*}{UTF8}{gbsn}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Jaime Trovoada}}\\
  \href{https://jaimetrovoada.vercel.app/}{Portfolio: jaimetrovoada.vercel.app}  & Email: \href{mailto:jaimetrovoada@gmail.com}{jaimetrovoada@gmail.com}\\
  \href{https://github.com/jaimetrovoada}{Github: github.com/jaimetrovoada} & Mobile: \href{tel:+8618202617004}{+86 182 0261 7004}\\
  \href{https://www.linkedin.com/in/jaimetrovoada630/}{LinkedIn: linkedin.com/in/jaimetrovoada630} & \textit{Lisbon, Portugal}\\
\end{tabular*}

%-----------EXPERIENCE-----------------
\vspace{5pt}
\section{\textcolor[HTML]{E36C09}{\textbf{EXPERIENCE}}}
\resumeSubHeadingListStart{}
    \resumeSubheading{Frontend Developer (Full-time)}{Beijing, China}
    {Beijing Burning Star Technology Co., Ltd.}{August 2021 - August 2022}
    \resumeItemListStart{}
        \item{Used Storybook to create reusable and maintainable components.}
        \item{Collaborated with a team of developers and designers to create a consistent and user-friendly design system.}
        \item{Proven ability to learn new technologies and adapt to change.}
        \item{Helped introduce tools like ESLint and Prettier to the team, thus improving code quality.}
    \resumeItemListEnd{}
\resumeSubHeadingListEnd{}


%-----------EDUCATION-----------------
\vspace{5pt}
\section{\textcolor[HTML]{E36C09}{\textbf{EDUCATION}}}
\resumeSubHeadingListStart{}
\resumeSubheading{Tianjin University}{Tianjin, China}
      {Bachelor, Computer Science}{September 2017 - July 2023}
      \resumeSubheading{Tianjin University}{Tianjin, China}
      {Chinese Language}{February 2017 - July 2017}
      \resumeSubheading{Fu Jen Catholic University}{Taiwan}
      {Chinese Language}{September 2016 - February 2017}
\resumeSubHeadingListEnd{}
	    

%-----------CERTS-----------------
\vspace{5pt}
\section{\textcolor[HTML]{E36C09}{\textbf{AWARDS \& CERTIFICATIONS}}}
\resumeSubHeadingListStart{}
\resumeSubheading{CSC - University Scholarship}{China Scholarship Council}
{Tianjin University}{2017 - 2021}
\resumeSubheading{\href{https://studies.cs.helsinki.fi/stats/api/certificate/fullstackopen/en/c54941f0ecb4d052a3cf6982d1d27398}{University of Helsinki - MOOC}}{fullstackopen.com}
{Full Stack Development}{2023}
\resumeSubHeadingListEnd{}

%-----------SKILLS-----------------
\vspace{5pt}
\section{\textcolor[HTML]{E36C09}{\textbf{TECHNOLOGIES \& SKILLS}}}
\resumeSubHeadingListStart{}
	  \resumeSubItem{Technical}{\quad JavaScript/TypeScript, React, NextJS, TailwindCSS, HTML/CSS/SCSS, Git, Go(lang), NodeJS/Express, SQL (PostgreSQL, MySQL)}
	  \resumeSubItem{Languages}{\quad Portuguese, English, Chinese (HSK4)}
    \resumeSubHeadingListEnd{}


%-----------PROJECTS-----------------
\vspace{5pt}
\section{\textcolor[HTML]{E36C09}{\textbf{PROJECTS}} \tiny{(more on my GitHub)}}
\resumeSubHeadingListStart{}
      \resumeSubItem{Got Food [TypeScript, NextJS, NodeJS/Express, TypeORM, PostgreSQL]}
      {A platform where restaurant owners can add their businesses so that customers can easily order their food when inside the facilities, without having to wait for a waiter.}
      \begin{itemize}
        \item{Implemented a JSON Web Token (JWT) authentication system, that allows users to log in using a email and password.}
        \item{Implemented an authorization service to verify what actions users are allowed to perform based on their roles.}
        \item{Implemented CRUD operations for managing user accounts, restaurants, menu items, and orders.}
        \item{Implemented upload service, that stores iamges to Firebase object storage, using Multer.}
      \end{itemize}
      \vspace{2pt}
      \resumeSubItem{GruvIt [React, TypeScript, Go, Docker]}
      {Developed a service that modifies uploaded pictures to the \href{https://github.com/morhetz/gruvbox}{gruvbox color palette} with the help of \href{https://github.com/paulopacitti/gruvbox-factory}{gruvbox-factory} python package and then serves it back to the user.}
      \vspace{2pt}
      \resumeSubItem{AppliTrackr [TypeScript, NextJS, Prisma, PostgreSQL]}
      {An job application tracker.}
      \begin{itemize}
        \item{Implemented OAuth based login system using Next-Auth, that allows users to sign using Google or Github.}
        \item{Used Tanstack/React-Tables to implement an auctionable/editable table that allows users to create and edit jobs.}
        \item{Implemented an analytics service to help users keep track of their progress.}
      \end{itemize}
      \vspace{2pt}
      \resumeSubItem{NittMngr [TypeScript, NextJS, Prisma, PostgreSQL]}
      {A feed manager for Nitter.}
      \vspace{2pt}
      \resumeSubItem{Patent Inquiry System [React, NodeJS, Express, and MySQL]}
      {Implemented a Backend/Server connected to a MySQL database and the Frontend for a service that contains information related to Patents and allows users to search for information contained in it.}
      \vspace{2pt}
\resumeSubHeadingListEnd{}

%-----------Hobbies and Interests-----------------
\vspace{5pt}
\section{\textcolor[HTML]{E36C09}{\textbf{HOBBIES AND INTERESTS}}}
\par{Besides working on my projects and keeping up with the latest news in the tech world, I enjoy playing video games, skateboarding, listening to music and going out to find new interesting places.}

\clearpage\end{CJK*}
\end{document}
